Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex

The time-dependence of the responses generates an interesting issue for interpretation. The first year responses are illustrative of the short-term immediate impacts of change, whereas the longer-term responses are heavily dominated by the feedback responses. Further, depiction of absolute vs. relative differences can serve to highlight different aspects of the model response. Here we report values from 15-20 years after fertilization began, to be consistent with the methodology used by \cite{wieder2019} in their analysis of global fertilization of the default model, and to capture the dynamics of the whole system feedbacks captured in Fig. \ref{timescales}.

Figures \ref{GPP CO2 and N responses 2001}, \ref{NPP CO2 and N respones 2001} and \ref{LAI CO2 and N respones 2001} illustrate the responses to both N and to CO$_{2}$ fertilization simultaneously, for GPP, NPP and, LAI. Corresponding figures for vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1 and 2). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).

\subsubsection{Impact of parameters}
Across the four sites, parametric impacts on fertilization responses were very varied, when compared to the relatively consistent impact of parameters on the initial system state. A majority of parameters show no consistent relationship with CO$_{2}$ or N deposition responses across sites, and the range of their impacts varied over an order of magnitude. Thus, the parameter response space of the model is complex with regard to these changing initial conditions, environments, and drivers on global change. Again, we go through the parameters one at a time to highlight the primary features of the model response and how they relate to expectations based on model structure.

@@

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parameteric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on gross primary productivity (GPP). }
     \label{GPP_CN_2016}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on net primary productivity (NPP).}
     \label{NPP_CN_2016}
  \end{figure}

  \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on leaf area index (LAI).}
     \label{LAI_CN_2016}
  \end{figure}

>>>>

The time-dependence of the responses generates an interesting issue for interpretation. The first year responses are illustrative of the short-term immediate impacts of change, whereas the longer-term responses are heavily dominated by the feedback responses. Further, depiction of absolute vs. relative differences can serve to highlight different aspects of the model response. Here we report values from 15-20 years after fertilization began, to be consistent with the methodology used by \cite{wieder2019} in their analysis of global fertilization of the default model, and to capture the dynamics of the whole system feedbacks captured in Fig. \ref{timescales}.  Thus, figures \ref{GPP_CN} and \ref{LAI_CN} illustrate the responses to 15-20 years of CO$_{2}$ and N  fertilization simultaneously, for GPP and LAI. Corresponding figures for NPP, vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1-3). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).

\subsubsection{Impact of parameters}
 the parameter response space of the model is complex with regard to these changing initial conditions, environments, and drivers on global change. Again, we go through the parameters one at a time to highlight the primary features of the model response and how they relate to expectations based on model structure.

@@

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parameteric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on gross primary productivity (GPP). }
     \label{GPP_CN}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on net primary productivity (NPP).}
     \label{NPP_CN}
  \end{figure}

  \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_TLAI_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on leaf area index (LAI).}
     \label{LAI_CN}
  \end{figure}
